Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{NSF Grant ???} }

### 2021-03-31 paper/paper_new.tex
Edited Section 6.

\begin{figure}[t]
  \centering
  \includegraphics[width=0.49\linewidth]{images/011196_pred}
  \includegraphics[width=0.49\linewidth]{images/011196_mask}
  \includegraphics[width=0.49\linewidth]{images/52399_pred}
  \includegraphics[width=0.49\linewidth]{images/52399_mask}
  \includegraphics[width=0.49\linewidth]{images/56885_pred}
  \includegraphics[width=0.49\linewidth]{images/56885_mask}
  \caption{Examples of masks and bounding boxes from detectron (left) and pixel analysis (right).}
\end{figure}

\subsection{Mask and Bounding Box}
Fish bounding boxes were calculated for all \(7,237\) images in which a fish was found. All but 263 of these were generated via pixel analysis, with those 263 falling back to the original \verb|detectron| bounding box.
50 randomly-chosen images were reviewed manually to evaluate the
calculation.  All 50 masks and bounding boxes were correctly placed
on/around the location of the fish. However, a number of them lacked portions of lightly colored tails and/or fins.
Specifically, 22 masks and bounding boxes covered the entire fish,
16 missed some of the tail, and 12 missed most or all of the tail.

@@

\section{Discussion}
\textbf{Todo}: Will need some sort of intro/framing paragraph
%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation. Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
%Discussion needed to weave in at least a couple of citations. Happy to discuss
\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
\subsubsection{Object Detection}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/none1}
  \includegraphics[width=0.49\linewidth]{images/double1}
  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
\end{figure}

\begin{itemize}
    \item Worked fairly well all things considered
    \item Talk about which fish failed
    \item Talk about which rulers failed
\end{itemize}
\subsubsection{Side Detection}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
\end{figure}
For all 6 of the cases where an eye was detected but the \verb|side| value was wrong, a spot on the wrong side of the fish was labeled as the most likely eye within the bounding box of the fish. There were an additional 17 images for which the automated process generated a result that did not match the manually created data. For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than than the human error rate.

\subsubsection{Clock Value}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/curved1}
  \caption{An example of a heavily curved specimen.}
\end{figure}
Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).For 25 of those the human generated data was incorrect, giving the automated process a \(3.1\) times lower error rate. Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value. The other 6 were values of 3 instead of 9 or vice versa that resulted from a mislabeled eye as discussed in the previous section. A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish. These tags were light enough that they were correctly labeled as background by the pixel analysis.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.49\linewidth]{images/011196_pred}
  \includegraphics[width=0.49\linewidth]{images/011196_mask}
  \includegraphics[width=0.49\linewidth]{images/52399_pred}
  \includegraphics[width=0.49\linewidth]{images/52399_mask}
  \includegraphics[width=0.49\linewidth]{images/56885_pred}
  \includegraphics[width=0.49\linewidth]{images/56885_mask}
  \caption{Examples of masks and bounding boxes from detectron (left) and pixel analysis (right).}
  \label{fig:bbox_mask}
\end{figure}

\subsection{Mask and Bounding Box}
Fish bounding boxes were calculated for all \(7,237\) images in which a fish was found. All but 263 of these were generated via pixel analysis, with those 263 falling back to the original \verb|detectron| bounding box.
50 randomly-chosen images were reviewed manually to evaluate the
calculation, a representative sample are presented in
Figure \ref{fig:bbox_mask}.
All 50 masks and bounding boxes were correctly placed
on/around the location of the fish. However, a number of them lacked portions of lightly colored tails and/or fins.
Specifically, 22 masks and bounding boxes covered the entire fish,
16 missed some of the tail, and 12 missed most or all of the tail.

@@

\section{Discussion}
\textbf{Todo}: Will need some sort of intro/framing paragraph
%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation. Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
%Discussion needed to weave in at least a couple of citations. Happy to discuss
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/none1}
  \includegraphics[width=0.49\linewidth]{images/double1}
  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
\end{figure}
\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
\subsubsection{Object Detection}

\begin{itemize}
    \item Worked fairly well all things considered
    \item Talk about which fish failed
    \item Talk about which rulers failed
\end{itemize}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
\end{figure}
\subsubsection{Side Detection}
There were six cases where an eye was detected but the \verb|side| value
was wrong. Here, a spot on the wrong side of the fish was labeled as the
most likely eye within the bounding box of the fish, i.e.~eye detection 
was incorrect.
There were an additional 17 images for which the automated process generated a result that did not match the manually created data. For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
This result highlights the additional utility of automated methods to
double-check and verify human-generated metadata.

\subsubsection{Clock Value}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/curved1}
  \caption{An example of a heavily curved specimen.}
  \label{fig:curvedFish}
\end{figure}
Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate. Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
seen in Figure \ref{fig:curvedFish}.
The other 6 were values of 3 instead of 9 or vice versa, which resulted from
a mislabeled eye as discussed in the previous section.
\todo{Why is the following sentence here? What does it have to do with
Clock Value?}
A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish. These tags were light enough that they were correctly labeled as background by the pixel analysis.
